Equalizer\\Programming and User Guide

### 2012-04-11 Developer/ProgrammingGuide/paper.tex
Minor PG revision

\begin{wrapfigure}{r}{.618\textwidth}
  \includegraphics[width=.618\textwidth]{images/netObject.pdf}
  {\caption{\label{fNetObject}Communication between two Objects}}
\end{wrapfigure}
Multiple instances of the same object (identifier) can be mapped on the same
node and session simultaneously. Each object instance has a node-unique instance
identifier. When the instance ID is set to \textsf{EQ\_INSTANCE\_ALL} (the
default value), a command is dispatch to all object instances registered to the
session with the correct object ID. Multiple object instance per node are used
when different threads on the node need to process a different version of the
same object.

When the packet is intended for a specific instance, set the instance identifier
of the object packet to the corresponding value.

@@

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_DRAWABLE\\
  \textbf{Value} & window \textbar \ pbuffer \textbar \ FBO\\
  \textbf{Default} & window\\
  \textbf{Details} & Selects the window's drawable type. A window is an
  on-screen, window system-dependent window with a full-window OpenGL
  drawable. PBuffers are off-screen drawables created using window
  system-dependent PBuffer API's. FBO are off-screen frame buffer
  objects. To calculate the PBuffer or FBO size on unconnected devices,
  a pipe viewport size of 4096x4096 is assumed,
  unless specified otherwise using the pipe's viewport parameter.\\
  \hline
\end{tabularx}\\\vfill

>>>>

Multiple instances of the same object (identifier) can be mapped on the same
node and session simultaneously. Each object instance has a node-unique instance
identifier. When the instance ID is set to \textsf{EQ\_INSTANCE\_ALL} (the
default value), a command is dispatch to all object instances registered to the
session with the correct object ID. Multiple object instance per node are used
when different threads on the node need to process a different version of the
same object.

\begin{wrapfigure}{r}{.618\textwidth}
  \includegraphics[width=.618\textwidth]{images/netObject.pdf}
  {\caption{\label{fNetObject}Communication between two Objects}}
\end{wrapfigure}
When the packet is intended for a specific instance, set the instance identifier
of the object packet to the corresponding value.

@@

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_WINDOW\_IATTR\_HINT\_DRAWABLE\\
  \textbf{Value} & window \textbar \ pbuffer \textbar \ FBO \textbar \ OFF\\
  \textbf{Default} & window\\
  \textbf{Details} & Selects the window's drawable type. A window is an
  on-screen, window system-dependent window with a full-window OpenGL
  drawable. PBuffers are off-screen drawables created using window
  system-dependent PBuffer API's. FBO are off-screen frame buffer
  objects. A disabled drawable creates a system window without a frame buffer
  for context sharing, e.g., for asynchronous operations in a separate
  thread. To calculate the PBuffer or FBO size on unconnected devices, a pipe
  viewport size of 4096x4096 is assumed, unless specified otherwise using the
  pipe's viewport parameter.\\
  \hline
\end{tabularx}\\\vfill
